Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-09-28 manuscript.qmd
Testing autobuild on group level analysis

processdata <- 0
# the processdata flag has three levels:
# 0 - just produce the manuscript with minimal analysis, using existing figures
# 1 - do group-level analysis using pre-computed MVPA and ERPs (requires 200MB)
# 2 - do all analyses from scratch using the raw data (requires ~35GB)

@@

Individuals with neurodevelopmental disorders such as attention deficit hyperactivity disorder (ADHD) and autism present with deficits in attention (American Psychiatric Association, 2013; [@Allen2001]. It has been suggested that repetitive stereotypies, or 'stimming' behaviours, are linked to these deficits in attention -- in the few studies where they have been asked, individuals who stim report that it benefits their ability to focus, and that the behaviours aid in emotional regulation [@Kapp2019; @Steward2015]. It has been proposed that an improved ability to focus through stimming may have a neural basis [@McCarty2021]. Building on these theories and research, we tested the effect of stimming on performance in a Posner cueing task.

>>>>

processdata <- 1
# the processdata flag has three levels:
# 0 - just produce the manuscript with minimal analysis, using existing figures
# 1 - do group-level analysis using pre-computed MVPA and ERPs (requires 200MB)
# 2 - do all analyses from scratch using the raw data (requires ~35GB)

@@

Individuals with neurodevelopmental disorders such as attention deficit hyperactivity disorder (ADHD) and autism present with deficits in attention [@Allen2001]. It has been suggested that repetitive stereotypies, or 'stimming' behaviours, are linked to these deficits in attention -- in the few studies where they have been asked, individuals who stim report that it benefits their ability to focus, and that the behaviours aid in emotional regulation [@Kapp2019; @Steward2015]. It has been proposed that an improved ability to focus through stimming may have a neural basis [@McCarty2021]. Building on these theories and research, we tested the effect of stimming on performance in a Posner cueing task.
